A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 6_validation.tex
Zjenja: validation edits

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of our strategies 'Inwards distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'. 
These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
The 'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
While 
 we found no significant differences in the smoothness of the toolpaths generated by the other strategies.

>>>>

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of our strategies 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'. 
These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed'.

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
The Inward  'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
While 
 we found no significant differences in the smoothness of the toolpaths generated by the other strategies.
